In-silico molecular enrichment and clearance of the human intracranial space

### 2025-06-05 paper/main.tex
Updates

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{figures/figure3a.png}
    \caption{\textbf{A static pressure gradient and peristaltic pumping are potential drivers of perivascular flow.}
    A) Surface arterial network colored by arterial radius with vessel locations labeled;
    B) Net PVS flow induced by CSF production (cf.~\Cref{fig:csf}
    -- histograms show the relative frequencies of local periarterial velocities. Positive values indicate antegrade PVS flow, while negative values indicate retrograde PVS flow;
    C) Illustration of the concept of peristaltic pumping;
    D) histograms of estimated net PVS flow induced by pulse wave or vasomotion peristaltic pumping;
    E) Estimated net PVS flow induced by pulse wave peristaltic pumping.
    F) Estimated net PVS flow induced by vasomotion/slow wave peristaltic pumping.}
    \label{fig:pvs_a}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{figures/figure3a.png}
    \caption{\textbf{A static pressure gradient and peristaltic pumping are potential drivers of perivascular flow.}
    A) Surface arterial network colored by arterial radius with vessel locations labeled;
    B) Net PVS flow induced by CSF production alone (see also ~\Cref{fig:csf}D).
    Histograms show the relative frequencies of local periarterial velocities. Positive values indicate antegrade PVS flow, while negative values indicate retrograde PVS flow;
    C) Illustration of the concept of peristaltic pumping;
    D) histograms of estimated net PVS flow induced by pulse wave or vasomotion peristaltic pumping;
    E) Estimated net PVS flow induced by pulse wave peristaltic pumping alone.
    F) Estimated net PVS flow induced by vasomotion/slow wave peristaltic pumping alone.}
    \label{fig:pvs_a}
\end{figure}
